Typing a linear \picalc

### 2020-03-25 paper/paper.tex
Add index to capability proof

% Constructors
\newcommand{\PO}{\constr{\mathbf{0}}}
\newcommand{\comp}[2]{#1 \; \constr{\parallel} \; #2}
\newcommand{\new}{\constr{\boldsymbol{\nu}} \;}
\newcommand{\send}[2]{#1 \; \constr{\langle}#2\constr{\rangle} \;}
\newcommand{\recv}[1]{#1 \; \constr{\mathbb{()}} \;}
\newcommand{\suc}{\constr{\scriptstyle 1+}}

@@

% Types
\newcommand{\reduce}[1]{\; \type{\longrightarrow}_{#1} \;}
\newcommand{\types}[4]{#1 \; \type{\propto} \; #2 \; \type{\vdash} \; #3 \; \type{\boxtimes} \; #4}
\newcommand{\contains}[5]{#1 \; \type{\propto} \; #2 \; \type{\ni} \; #3 \; \type{\propto} \; #4 \; \type{\boxtimes} \; #5}
\newcommand{\Var}{\type{VAR}}
\newcommand{\Process}{\type{PROCESS}}
\newcommand{\Unused}{\type{UNUSED}}
\newcommand{\PreCtx}{\type{PRECTX}}
\newcommand{\Ctx}{\type{CTX}}
\newcommand{\Type}{\type{TYPE}\;}
\newcommand{\Idx}{\type{IDX}\;}
\newcommand{\Idxs}{\type{IDXS}}
\newcommand{\Carrier}{\type{CARRIER}}
\newcommand{\N}{\type{\mathbb{N}}}
\newcommand{\Channel}{\type{CHANNEL}}
\newcommand{\Rec}{\type{REC}}
\newcommand{\Quantifier}{\type{QUANTIFIER}}
\newcommand{\eq}[1]{\; \type{=}_{#1} \;}
\newcommand{\eqeq}{\; \type{\equiv} \;}

@@

\begin{figure}[h]
  \begin{mathpar}
    {\mprset{fraction={===}}
      \inferrule
      { }
      {\type{\N} : \type{Set}}}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    {n : \N}
    {\Var_n : Set}}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    {n : \N}
    {\Process_n : Set}}
\end{mathpar}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    { }
    {P \eqeq Q : Set}}

@@

  {\mprset{fraction={===}}
    \inferrule
    { }
    {\Rec : Set}}

@@

  {\mprset{fraction={===}}
    \inferrule
    {P \, Q : \Process_n \\ r : \Rec}
    {P \eq{r} Q : Set}}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    {n : \N}
    {\Channel_n : Set}}

@@

  {\mprset{fraction={===}}
    \inferrule
    {i : \Channel_n \\ P \; Q : \Process_n}
    {P \reduce{i} Q : Set}}

@@

\begin{figure}[h]
\begin{equation}
\begin{aligned}
  &\lz                    &:{} &                      &     & C \\
  &\li                    &:{} &                      &     & C \\
  &\lo                    &:{} &                      &     & C \\
  &\op{\_}{\_}{\_}        &:{} &                      &     & C \to C \to C \to Set \\
  &\field{\cdot-join}     &:{} &                      &     & \type{\exists} \lio . \; \op{\lio}{\li}{\lo} \\
  &\field{\cdot-compute}  &:{} &\forall y z           & \to & \type{Dec} \; (\type{\exists} x . \; (\op{x}{y}{z})) \\
  &\field{\cdot-unique}   &:{} &\forall \{x x' y z\}  & \to & \op{x'}{y}{z} \to \op{x}{y}{z} \to x' \equiv x \\
  &\field{\cdot-unique^l} &:{} &\forall \{x y y' z\}  & \to & \op{x}{y'}{z} \to \op{x}{y}{z} \to y' \equiv y \\
  &\field{\cdot-id^l}     &:{} &\forall x             & \to & \op{x}{\lz}{x} \\
  &\field{\cdot-comm}     &:{} &\forall \{x y z\}     & \to & \op{x}{y}{z} \to \op{x}{z}{y} \\
  &\field{\cdot-assoc}    &:{} &\forall \{x y z u v\} & \to & \op{x}{y}{z} \to \op{y}{u}{v} \to \type{\exists} w . \; (\op{x}{u}{w} \times \op{w}{v}{z})
\end{aligned}
\end{equation}
\caption{Quantifier algebra $\Quantifier_C$ algebra on a partial commutative monoid with special elements $\ell_i$, $\ell_o$ and $\ell_\#$.}
\label{capabilities}
\end{figure}

@@

\begin{figure}[h]
\begin{equation}
\begin{split}
  \field{IDX}          &: Set \\
  \field{\exists IDX}  &: \field{IDX} \\
  \field{CARRIER}      &: \field{IDX} \to Set \\
  \field{QUANTIFIERS}  &: (i : \field{IDX}) \to \Quantifier_{\field{CARRIER}_i}
\end{split}
\end{equation}
\caption{Indexed set of partial commutative monoids}
\label{indexed-capabilities}
\end{figure}

@@

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    {n : \N}
    {\PreCtx_n : Set}
  }

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    {n : \N}
    {\Idxs_n : Set}}

@@

  {\mprset{fraction={===}}
    \inferrule
    {is : \Idxs_n}
    {\Ctx_{is} : Set}}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule{
      \gamma : \PreCtx_n \\
      \inferrule*{}{
        is : \Idxs_n \\\\
        \Gamma : \Ctx_{is}} \\
      t : \Type \\
      x : \Carrier_i \\
      \Delta : \Ctx_{is}}
    {\contains{\gamma}{\Gamma}{t}{x}{\Delta} : Set}}

@@

  {\mprset{fraction={===}}
    \inferrule{
      \gamma : \PreCtx_n \\
      \inferrule*{}{
        is : \Idxs_n \\\\
        \Gamma : \Ctx_{is}} \\
      P : \Process_n \\
      \Delta : \Ctx_{is}}
    {\types{\gamma}{\Gamma}{P}{\Delta} : Set}}

@@

  \inferrule
  {t : \Type \\ x : \Carrier_i \\ y : \Carrier_j \\\\
   cont : \types{\gamma , C[ t \propto x ]}{\Gamma , y}{P}{\Delta , 0.}}
  {\constr{chan} \; t \; x \; y : \types{\gamma}{\Gamma}{\new P}{\Delta}}

  \inferrule
  {chan_x : \contains{\gamma}{\Gamma}{C[ t \propto x]}{+\cdot}{\Xi} \\\\
   cont : \types{\gamma , t}{\Xi , x}{P}{\Theta , 0\cdot}}
  {\constr{recv} \; chan_x \; cont : \types{\gamma}{\Gamma}{\recv{toFin \; chan_x}{P}}{\Theta}}

  \inferrule
  {chan_x : \contains{\gamma}{\Gamma}{C[t \propto x]}{-\cdot}{\Delta} \\\\
   loc_y : \contains{\gamma}{\Delta}{t}{x}{\Xi} \\\\
   cont : \types{\gamma}{\Xi}{P}{\Theta}}
  {\constr{send} \; chan_x \; loc_y \; cont : \types{\gamma}{\Gamma}{\send{toFin \; chan_x}{toFin \; loc_y}P}{\Theta}}

>>>>

% Constructors
\newcommand{\PO}{\constr{\mathbf{0}}}
\newcommand{\comp}[2]{#1 \; \constr{\parallel} \; #2}
\newcommand{\new}{\constr{\boldsymbol{\nu}} \;}
\newcommand{\send}[2]{#1 \; \constr{\langle}#2\constr{\rangle} \;}
\newcommand{\recv}[1]{#1 \; \constr{\mathbb{()}} \;}
\newcommand{\suc}{\constr{\scriptstyle 1+}}
\newcommand{\base}[1]{\constr{B[} \; #1 \; \constr{]}}
\newcommand{\channel}[2]{\constr{C[} \; #1 \; \constr{\propto} \; #2 \; \constr{]}}

@@

% Types
\newcommand{\Set}{\type{SET}}
\newcommand{\reduce}[1]{\; \type{\longrightarrow}_{#1} \;}
\newcommand{\types}[4]{#1 \; \type{\propto} \; #2 \; \type{\vdash} \; #3 \; \type{\boxtimes} \; #4}
\newcommand{\contains}[5]{#1 \; \type{\propto} \; #2 \; \type{\ni} \; #3 \; \type{\propto} \; #4 \; \type{\boxtimes} \; #5}
\newcommand{\Var}{\type{VAR}}
\newcommand{\Process}{\type{PROCESS}}
\newcommand{\Unused}{\type{UNUSED}}
\newcommand{\PreCtx}{\type{PRECTX}}
\newcommand{\Ctx}{\type{CTX}}
\newcommand{\Type}{\type{TYPE}\;}
\newcommand{\Idx}{\type{IDX}\;}
\newcommand{\Idxs}{\type{IDXS}}
\newcommand{\Carrier}{\type{CARRIER}}
\newcommand{\N}{\type{\mathbb{N}}}
\newcommand{\Channel}{\type{CHANNEL}}
\newcommand{\Rec}{\type{REC}}
\newcommand{\Quantifier}{\type{QUANTIFIER}}
\newcommand{\eq}[1]{\; \type{=}_{#1} \;}
\newcommand{\eqeq}{\; \type{\equiv} \;}

@@

\begin{figure}[h]
  \begin{mathpar}
    {\mprset{fraction={===}}
      \inferrule
      { }
      {\type{\N} : \Set}}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    {n : \N}
    {\Var_n : \Set}}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    {n : \N}
    {\Process_n : \Set}}
\end{mathpar}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    { }
    {P \eqeq Q : \Set}}

@@

  {\mprset{fraction={===}}
    \inferrule
    { }
    {\Rec : \Set}}

@@

  {\mprset{fraction={===}}
    \inferrule
    {P \, Q : \Process_n \\ r : \Rec}
    {P \eq{r} Q : \Set}}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    {n : \N}
    {\Channel_n : \Set}}

@@

  {\mprset{fraction={===}}
    \inferrule
    {i : \Channel_n \\ P \; Q : \Process_n}
    {P \reduce{i} Q : \Set}}

@@

\begin{figure}[h]
\begin{equation}
\begin{aligned}
  &\lz                    &:{} &                      &        & C \\
  &\li                    &:{} &                      &        & C \\
  &\lo                    &:{} &                      &        & C \\
  &\op{\_}{\_}{\_}        &:{} &                      &        & C \to C \to C \to \Set \\
  &\field{\cdot-join}     &:{} &                      &        & \type{\exists} \lio . \; \op{\lio}{\li}{\lo} \\
  &\field{\cdot-compute}  &:{} &\forall y z           & \to \; & \type{DEC} \; (\type{\exists} x . \; (\op{x}{y}{z})) \\
  &\field{\cdot-unique}   &:{} &\forall \{x x' y z\}  & \to \; & \op{x'}{y}{z} \to \op{x}{y}{z} \to x' \equiv x \\
  &\field{\cdot-unique^l} &:{} &\forall \{x y y' z\}  & \to \; & \op{x}{y'}{z} \to \op{x}{y}{z} \to y' \equiv y \\
  &\field{\cdot-id^l}     &:{} &\forall x             & \to \; & \op{x}{\lz}{x} \\
  &\field{\cdot-comm}     &:{} &\forall \{x y z\}     & \to \; & \op{x}{y}{z} \to \op{x}{z}{y} \\
  &\field{\cdot-assoc}    &:{} &\forall \{x y z u v\} & \to \; & \op{x}{y}{z} \to \op{y}{u}{v} \to \type{\exists} w . \; (\op{x}{u}{w} \times \op{w}{v}{z})
\end{aligned}
\end{equation}
\caption{Quantifier algebra $\Quantifier_C$ algebra on a partial commutative monoid with special elements $\ell_i$, $\ell_o$ and $\ell_\#$.}
\label{capabilities}
\end{figure}

@@

\begin{figure}[h]
\begin{equation}
\begin{split}
  \field{IDX}          &: \Set \\
  \field{\exists IDX}  &: \field{IDX} \\
  \field{CARRIER}      &: \field{IDX} \to \Set \\
  \field{QUANTIFIERS}  &: (i : \field{IDX}) \to \Quantifier_{\field{CARRIER}_i}
\end{split}
\end{equation}
\caption{Indexed set of partial commutative monoids}
\label{indexed-capabilities}
\end{figure}

@@

\todo{mention types are independent from capabilities}
\todo{add index to in-type}
\todo{update examples}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    { }
    {\Type : \Set}
  }

  \inferrule
  {n : \N}
  {\base{n} : \Type}

  \inferrule
  {t : \Type \\ \inferrule*{} {i : \Idx \\\\ x : \Carrier_i}}
  {\channel{t}{x} : \Type}
\end{mathpar}
\caption{This is...}
\end{figure}

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    {n : \N}
    {\PreCtx_n : \Set}
  }

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule
    {n : \N}
    {\Idxs_n : \Set}}

@@

  {\mprset{fraction={===}}
    \inferrule
    {is : \Idxs_n}
    {\Ctx_{is} : \Set}}

@@

\begin{figure}[h]
\begin{mathpar}
  {\mprset{fraction={===}}
    \inferrule{
      \gamma : \PreCtx_n \\
      \inferrule*{}{
        is : \Idxs_n \\\\
        \Gamma : \Ctx_{is}} \\
      t : \Type \\
      x : \Carrier_i \\
      \Delta : \Ctx_{is}}
    {\contains{\gamma}{\Gamma}{t}{x}{\Delta} : \Set}}

@@

  {\mprset{fraction={===}}
    \inferrule{
      \gamma : \PreCtx_n \\
      \inferrule*{}{
        is : \Idxs_n \\\\
        \Gamma : \Ctx_{is}} \\
      P : \Process_n \\
      \Delta : \Ctx_{is}}
    {\types{\gamma}{\Gamma}{P}{\Delta} : \Set}}

@@

  \inferrule
  {t : \Type \\ x : \Carrier_i \\ y : \Carrier_j \\\\
   cont : \types{\gamma , \channel{t}{x}}{\Gamma , y}{P}{\Delta , \lz}}
  {\constr{chan} \; t \; x \; y \; cont : \types{\gamma}{\Gamma}{\new P}{\Delta}}

  \inferrule
  {chan_x : \contains{\gamma}{\Gamma}{\channel{t}{x}}{\li}{\Xi} \\\\
   cont : \types{\gamma , t}{\Xi , x}{P}{\Theta , \lz}}
  {\constr{recv} \; chan_x \; cont : \types{\gamma}{\Gamma}{\recv{toFin \; chan_x}{P}}{\Theta}}

  \inferrule
  {chan_x : \contains{\gamma}{\Gamma}{\channel{t}{x}}{\lo}{\Delta} \\\\
   loc_y : \contains{\gamma}{\Delta}{t}{x}{\Xi} \\\\
   cont : \types{\gamma}{\Xi}{P}{\Theta}}
  {\constr{send} \; chan_x \; loc_y \; cont : \types{\gamma}{\Gamma}{\send{toFin \; chan_x}{toFin \; loc_y}P}{\Theta}}
